\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\section{Measure-valued Proximal Recursion}\label{sec:prox}
\subsection{Generalized Gradient Descent}\label{subsec:GenGradDescent}
Let $\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right)$ denote the manifold of all joint PDFs supported over the state space $\mathbb{T}^{n} \times \mathbb{R}^{n}$, with finite second raw moments. Symbolically,
\begin{align}
\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right) := &\bigg\{\rho : \mathbb{T}^{n} \times \mathbb{R}^{n} \mapsto \mathbb{R}_{\geq 0} \mid \int \rho = 1,\nonumber\\
&\hspace*{-0.8in}\int\bm{x}^{\top}\bm{x}\:\rho(\bm{x})\:\differential\bm{x} <\infty\; \text{for all}\;\bm{x}\equiv(\bm{\theta},\bm{\omega})^{\top}\in\mathbb{T}^{n} \times \mathbb{R}^{n} \bigg\}.
\label{DefP2}	
\end{align}
We propose to solve the initial value problem for the PDE \eqref{KineticFPK} by viewing its flow $\rho(t,\bm{\theta},\bm{\omega})$ as the gradient descent of some functional $\Phi:\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right)\mapsto \mathbb{R}_{\geq 0}$ w.r.t. some distance 
\[{\rm{dist}}:\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right)\times\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right)\mapsto\mathbb{R}_{\geq 0}.\]
We now explain this idea in detail.

@@

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)^{\top}$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta}_{k}^{i},\bm{\omega}_{k}^{i}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right) \nonumber\\
&= \left(\prod_{j=1}^{n}m_{j}/\sigma_{j}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta}_{k}^{i},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}_{k}^{i}\right),
\label{BringBackOriginalStateSpace}	
\end{align}
for all $i=1,\hdots,N$. The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}. For completeness, the overall algorithm is {\red{given}}.

>>>>

\section{Measure-valued Proximal Recursion}\label{sec:prox}
\subsection{Generalized Gradient Descent}\label{subsec:GenGradDescent}
Let $\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right)$ denote the manifold of joint PDFs supported over the state space $\mathbb{T}^{n} \times \mathbb{R}^{n}$, with finite second raw moments. Symbolically,
\begin{align}
\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right) := &\bigg\{\rho : \mathbb{T}^{n} \times \mathbb{R}^{n} \mapsto \mathbb{R}_{\geq 0} \mid \int \rho = 1,\nonumber\\
&\hspace*{-0.8in}\int\bm{x}^{\top}\bm{x}\:\rho(\bm{x})\:\differential\bm{x} <\infty\; \text{for all}\;\bm{x}\equiv(\bm{\theta},\bm{\omega})^{\top}\in\mathbb{T}^{n} \times \mathbb{R}^{n} \bigg\}.
\label{DefP2}	
\end{align}
We propose to solve the initial value problem for the PDE \eqref{KineticFPK} by viewing its flow $\rho(t,\bm{\theta},\bm{\omega})$ as the gradient descent of some functional $\Phi:\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right)\mapsto \mathbb{R}_{\geq 0}$ w.r.t. some distance 
\[{\rm{dist}}:\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right)\times\mathcal{P}_{2}\left(\mathbb{T}^{n} \times \mathbb{R}^{n}\right)\mapsto\mathbb{R}_{\geq 0}.\]
We now explain this idea in detail.

@@

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)^{\top}$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta}_{k}^{i},\bm{\omega}_{k}^{i}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right) \nonumber\\
&= \left(\prod_{j=1}^{n}m_{j}/\sigma_{j}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta}_{k}^{i},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}_{k}^{i}\right),
\label{BringBackOriginalStateSpace}	
\end{align}
for all $i=1,\hdots,N$. The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}. For completeness, the overall proximal algorithm is {\red{given}}.
